Scheduling and Amortization for MPC

### 2022-02-19 biometric_vectorization_example.tex
Minor edit to Biometric example section formatting.
Minor edit to Basic Vectorization.

\subsubsection{Benjamin's code with linear loops (MPC Source)}

@@

{\small
\begin{verbatim}
min_sum!1 = 10000
min_sum!1^ = raise_dim(min_sum!1, (i:N!0))
min_index!1 = 0
min_index!1^ = raise_dim(min_index!1, (i:N!0))
S!0^ = raise_dim(S!0, ((i * D!0) + j), (i:N!0,j:D!0))
C!0^ = raise_dim(C!0, j, (i:N!0,j:D!0))
for i in range(0, N!0):
  min_sum!2[I] = PHI(min_sum!1^[I], min_sum!4[I]) 
  min_index!2[I] = PHI(min_index!1^[I], min_index!4[I])  
  sum!2 = [0,..,0] 
  sum!2^ = raise_dim(sum!2, (j:D!0))
  d!3[I,J] = S!0^[I,J] - C!0^[I,J]
  p!3[I,J] = (d!3[I,J] * d!3[I,J])
  for j in range(0, D!0):
    sum!3[I,j] = PHI(sum!2^[I,j], sum!4[I,j-1])       
    sum!4[I,j] = (sum!3[I,j] + p!3[I,j])
  sum!3^ = drop_dim(sum!3)     
  !1!2[I] = (sum!3^[I] < min_sum!2[I])
  min_sum!3 = sum!3^
  min_index!3 = [0,1,2,...,N!0-1]
  min_sum!4[I] = MUX(!1!2[I], min_sum!3[I], min_sum!2[I])
   min_index!4[I] = MUX(!1!2[I], min_index!3[I], min_index!2[I])
min_sum!2^ = drop_dim(min_sum!2)
min_index!2^ = drop_dim(min_index!2)   
!2!1 = (min_sum!2^, min_index!2^)
\end{verbatim}
}

@@

sum!3^ = drop_dim(sum!3)     
min_index!3 = [0,1,2,...N!0-1]   
min_sum!3 = sum!3^

>>>>

We start from Benjamin's code with linear loops (MPC Source):

@@

{\small
\begin{verbatim}
min_sum!1 = 10000
min_sum!1^ = raise_dim(min_sum!1, (i:N!0))
min_index!1 = 0
min_index!1^ = raise_dim(min_index!1, (i:N!0))
S!0^ = raise_dim(S!0, ((i * D!0) + j), (i:N!0,j:D!0))
C!0^ = raise_dim(C!0, j, (i:N!0,j:D!0))
for i in range(0, N!0):
  min_sum!2[I] = PHI(min_sum!1^[I], min_sum!4[I]) 
  min_index!2[I] = PHI(min_index!1^[I], min_index!4[I])  
  sum!2 = [0,..,0] 
  sum!2^ = raise_dim(sum!2, (j:D!0))
  d!3[I,J] = S!0^[I,J] - C!0^[I,J]
  p!3[I,J] = (d!3[I,J] * d!3[I,J])
  for j in range(0, D!0):
    sum!3[I,j] = PHI(sum!2^[I,j], sum!4[I,j-1])       
    sum!4[I,j] = (sum!3[I,j] + p!3[I,j])
  sum!3^ = drop_dim(sum!3)     
  !1!2[I] = (sum!3^[I] < min_sum!2[I])
  min_sum!3 = sum!3^
  min_index!3 = i
  min_sum!4[I] = MUX(!1!2[I], min_sum!3[I], min_sum!2[I])
   min_index!4[I] = MUX(!1!2[I], min_index!3[I], min_index!2[I])
min_sum!2^ = drop_dim(min_sum!2)
min_index!2^ = drop_dim(min_index!2)   
!2!1 = (min_sum!2^, min_index!2^)
\end{verbatim}
}

@@

sum!3^ = drop_dim(sum!3)     
min_index!3 = [0,1,2,...N!0-1] // or min_index!3 = [i, (i:N!0)]
min_sum!3 = sum!3^
